Descriptive analysis

### 2020-03-08 analysis/02_descriptive-analysis.Rmd
Ha, use predicted draws for real

diff_cs_pts_posterior <- canary %>% 
  filter(year == 2010) %>% 
  modelr::data_grid(PTS_factor) %>% 
  add_fitted_draws(diff_cs_pts, seed = BAYES_SEED)
```

@@

```{r plot-posterior-preds-pts-cs, fig.width=params$fig_width, fig.height=params$fig_height, warning=FALSE, message=FALSE}
ggplot(diff_cs_pts_posterior, aes(x = .value, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
  stat_dotsh(quantiles = 100, shape = 19) +
  stat_pointintervalh(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                          interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
  scale_x_reverse() +
  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Political Terror Scale (PTS)",
       caption = "Each • represents an equally likely outcome from the posterior distribution") +
  theme_ngo()

@@

diff_ngo_pts_posterior <- canary %>% 
  filter(year == 2010) %>% 
  modelr::data_grid(PTS_factor) %>% 
  add_fitted_draws(diff_ngo_pts, seed = BAYES_SEED)
```

@@

```{r plot-posterior-preds-pts-ngo, fig.width=params$fig_width, fig.height=params$fig_height, warning=FALSE, message=FALSE}
ggplot(diff_ngo_pts_posterior, aes(x = .value, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
  stat_dotsh(quantiles = 100, shape = 19) +
  stat_pointintervalh(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                          interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Number of restrictive NGO laws", y = "Political Terror Scale (PTS)",
       caption = "Each • represents an equally likely outcome from the posterior distribution") +
  theme_ngo()
```

@@

diff_cs_conflict_posterior <- canary %>% 
  filter(year == 2010) %>% 
  modelr::data_grid(armed_conflict) %>% 
  add_fitted_draws(diff_cs_conflict, seed = BAYES_SEED) %>% 
  ungroup() %>% 
  mutate(armed_conflict = factor(armed_conflict, labels = c("No armed conflict", "Armed conflict")))
```

@@

```{r plot-posterior-preds-conflict-cs, fig.width=params$fig_width, fig.height=params$fig_height, warning=FALSE, message=FALSE}
ggplot(diff_cs_conflict_posterior, aes(x = .value, y = fct_rev(armed_conflict), color = fct_rev(armed_conflict))) +
  stat_dotsh(quantiles = 100, shape = 19) +
  stat_pointintervalh(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                          interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
  scale_x_reverse() +
  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Armed conflict",
       caption = "Each • represents an equally likely outcome from the posterior distribution") +
  theme_ngo()

>>>>

diff_cs_pts_posterior <- canary %>% 
  filter(year == 2010) %>% 
  modelr::data_grid(PTS_factor) %>% 
  add_predicted_draws(diff_cs_pts, seed = BAYES_SEED)
```

@@

```{r plot-posterior-preds-pts-cs, fig.width=params$fig_width, fig.height=params$fig_height, warning=FALSE, message=FALSE}
ggplot(diff_cs_pts_posterior, aes(x = .prediction, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
  stat_dotsh(quantiles = 100, shape = 19) +
  stat_pointintervalh(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                          interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
  scale_x_reverse() +
  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Political Terror Scale (PTS)",
       caption = "Each • represents an equally likely outcome from the posterior distribution") +
  theme_ngo()

@@

diff_ngo_pts_posterior <- canary %>% 
  filter(year == 2010) %>% 
  modelr::data_grid(PTS_factor) %>% 
  add_predicted_draws(diff_ngo_pts, seed = BAYES_SEED)
```

@@

```{r plot-posterior-preds-pts-ngo, fig.width=params$fig_width, fig.height=params$fig_height, warning=FALSE, message=FALSE}
ggplot(diff_ngo_pts_posterior, aes(x = .prediction, y = fct_rev(PTS_factor), color = fct_rev(PTS_factor))) +
  stat_dotsh(quantiles = 100, shape = 19) +
  stat_pointintervalh(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                          interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Number of restrictive NGO laws", y = "Political Terror Scale (PTS)",
       caption = "Each • represents an equally likely outcome from the posterior distribution") +
  theme_ngo()
```

@@

diff_cs_conflict_posterior <- canary %>% 
  filter(year == 2010) %>% 
  modelr::data_grid(armed_conflict) %>% 
  add_predicted_draws(diff_cs_conflict, seed = BAYES_SEED) %>% 
  ungroup() %>% 
  mutate(armed_conflict = factor(armed_conflict, labels = c("No armed conflict", "Armed conflict")))
```

@@

```{r plot-posterior-preds-conflict-cs, fig.width=params$fig_width, fig.height=params$fig_height, warning=FALSE, message=FALSE}
ggplot(diff_cs_conflict_posterior, aes(x = .prediction, y = fct_rev(armed_conflict), color = fct_rev(armed_conflict))) +
  stat_dotsh(quantiles = 100, shape = 19) +
  stat_pointintervalh(aes(point_colour = after_scale(colorspace::darken(color, 0.65)),
                          interval_colour = after_scale(colorspace::darken(color, 0.35)))) +
  scale_x_reverse() +
  scale_color_viridis_d(option = "inferno", begin = 0.2, end = 0.9, guide = FALSE) +
  labs(x = "Civil society repression", y = "Armed conflict",
       caption = "Each • represents an equally likely outcome from the posterior distribution") +
  theme_ngo()
